Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2016-11-17 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Outline for 1st paper updated

	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
	\begin{itemize}
		\item Leading technologies and their limitations:
		\begin{itemize}
			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
			\item Zeolites - Good rejections/selectivities, but low flux and high cost of manufacturing. Generally limited to applications needing thermal/chemical resistance
		\end{itemize}
	\end{itemize}

	Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which are feasible for large scale production.
	\begin{itemize}
		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
		\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
		\item Hydrophilic regions point towards pore centers
		\item Until recently, they could not be aligned - hindered progress
		\item Talk about Yale alignment techniques
		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
	\end{itemize}

@@

	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item Small number of layers create micellar structure
		\item Beyond 20 layers is unnecessary to get expected configuration
	\end{itemize}

	The starting distance between layers was chosen so that energy minimization occured with no errors due to overlaps. 
	\begin{itemize}
		\item Layers close enough together to prevent layers from slipping between each other
		\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
	\end{itemize}

	\noindent The remaining parameters were chosen based on experimental data. 
	\begin{itemize}
		\item SAXS to get Pore-to-Pore
		\item TEM images estimate pore size
	\end{itemize}

	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
	% Include new equilibration scheme here? 
	\begin{itemize}
		\item Monitored 'hexagonality'
		\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
		\item We see a smaller average pore-to-pore distance than reported
		\item Varied initial pore-to-pore distance and ran very long simulations
		\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
	\end{itemize}

@@

	The final, equilibrated system had pores which were spaced 4.2 nm apart.
	\newline 
	\newline \noindent Questions to be answered and experiments to test them:

	\begin{itemize}
		\item Question: How many monomers are in each layer? Do we even see defined layers?
		\begin{itemize}
			\item \textbf{Why this is important:} 
				\item We can understand how monomer shape/size/length influence pore density
				\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
				\item We can see whether the effects of pi stacking are as pronounced as hypothesized in other papers.
					\item fixed-charge models may underpredict pi-stacking -- searching for a reference to confirm this although that would make sense. How would this limit what we can say about the pore structure?
			\item \textbf{Experiments to be run:}
				\item Use membrane thickness and approximate pore size to define cylindrical disk regions. Measure number of monomers in these regions
				\item Visualization will help too
			\item \textbf{Hypothesis:} There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature. While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains. Staying completely ordered, stacked on top of each other is not entropically favorable.
		\end{itemize}
		\item How do sodium counterions behave inside the pores and what influence might they have on membrane performance?
		\begin{itemize}
			\item \textbf{Why this is important:}
			\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulations show that they may be arranged gaussian-like	
			\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
			\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
			\item \textbf{Experiments to be run and what they can tell us:} 
				\item Measure Ionic Conductivity as a direct comparison to experiment -- speculate about the mechanism of ionic conduction and how it can be improved by changing the microscopic structure
				\item Measure Ionic Conduction on early equilibration membrane which shows defined pores
			\item \textbf{Hypothesis:} Sodium ions are arranged across each pore radius according to a gaussian distribution. This organization leads to higher ionic conductivity because ions are more mobile, while an ordered pore restricts the ability of ions to hop to different sites.
		\end{itemize}
		\item How can we validate the model?
		\begin{itemize}
			\item textbf{Why this is important:}
			\item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
			\item \textbf{Experiments to Run:}
			\item Direct comparison of conductivity measurements to experimental results
			\item SAXS structural comparisons
		\end{itemize} 
	\end{itemize}
	We can vary the following to make predictions about new systems:
		\begin{itemize}
			\item Liquid crystal used - or a mixture of different liquid crystals
			\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
			\item Counterion -- Size/valence of counterion
			\item Functional head groups
			\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed
		\end{itemize} 
	\section{Conclusion}

	In this work, a molecular model has been developed which can predict transport in an thermotropic liquid crystal membrane. 
	\begin{itemize}
		\item Results presented for HII phase monomer but can be adapted to other LCs
		\item Model can be used for prediction of transport properties in new membranes
	\end{itemize}

>>>>

	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
	\begin{itemize}
		\item Leading technologies and their limitations:
		\begin{itemize}
			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
		\end{itemize}
	\end{itemize}

	Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which are feasible for large scale production.
	\begin{itemize}
		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
		\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
		\item Hydrophilic regions point towards pore centers
		\item Until recently, they could not be aligned - hindered progress
		\item Yale aligns them
		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
	\end{itemize}

@@

	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item Small number of layers create micellar structure
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}

	\noindent The remaining parameters were chosen based on experimental data. 
	\begin{itemize}
		\item SAXS to get Pore-to-Pore
		\item TEM images and rejection give a pore size estimate
	\end{itemize}

	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
	\begin{itemize}
		\item Monitored 'hexagonality'
		\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
		\item We see a smaller average pore-to-pore distance than reported
		\item Varied initial pore-to-pore distance and ran very long simulations
		\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
	\end{itemize}

@@

	The validity of our model can be tested based on its agreement with experimental structural and material property data
	\begin{itemize}
		\item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
		\item Tougher with a large system for which no force fields have been specifically developed
		\item Direct comparison of conductivity measurements to experimental results
		\item SAXS structural comparisons
	\end{itemize}

	A structurally accurate and reproducible model of the Colh phase LLC membrane has been developed
	\begin{itemize}
		\item Visual perspective - show top view and cross section
		\item System validated using multiple monomer configurations (working on this now)
		\item Pore to pore distance
		\begin{itemize}
			\item We know from SAXS data what the distance between pores should be
			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
			\item Effect of crosslinking
		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
		\end{itemize}
	\end{itemize}

	The monomers are arranged into disks containing __ monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
	\begin{itemize}
		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature. While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains. Staying completely ordered, stacked on top of each other is not entropically favorable.
		\item We can understand how monomer shape/size/length influence pore density
		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.

	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian)
	\begin{itemize}
		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations show that they are not 	
		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
		\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.

	The model gives reasonable estimates of ionic conductivity.
	\begin{itemize}
		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
		\item We must also account for the azimuthal distributions, linking our perfectly straight microscopic system to the not-so-straight macroscopic system
		\item Two methods used to for prediction
		\item Nernst Einstein Relation:
		\begin{itemize}
			\item Widely used equation for estimating ionic conductivity
			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
			\item Concentration is concentration of ions in the whole membrane, not just channels
		\end{itemize}
		\item Collective Diffusion:
		\begin{itemize}
			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores. One would expect single channel IC to be much larger than the bulk membrane
			\item This model suggests that changing the structure of the monomer tails may actually improve conductivity (I don't know how feasible this would actually be, they'd need to be charged somehow) 
			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
	\end{itemize}

	Our model can be used to evaluate other liquid crystalline assemblies
		\begin{itemize}
			\item Liquid crystal used - or a mixture of different liquid crystals
			\item Minor structural variations (e.g. 7, 8, 9, 10, 11 ... CH2's in the tails)
			\item Counterion -- Size/valence of counterion
			\item Functional head groups
			\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed
		\end{itemize}

	\section{Conclusion}

	In this work, a molecular model has been developed which can predict transport in an thermotropic liquid crystal membrane. 
	\begin{itemize}
		\item Results presented for Colh phase monomer but can be adapted to other LCs
		\item Model can be used for prediction of transport properties in new membranes
		\item Yet to solvate system to establish procedures for HII phase prediction
	\end{itemize}
